\LARGE \bf Reactive Trajectory Planning and Trajectory Tracking for Pedestrian-Aware Autonomous Driving in Urban Environments

### 2016-01-22 root.tex
moved RSTOP trajectory planning stuff to another section

Next the nominal stopping distance $\Delta s_{RSTOP}$ must be computed given the vehicle's current location, speed, and forward acceleration.
The procedure for doing this will be the same as the procedure for planning the RSTOP later with a few steps omitted, since the planning algorithm is extremely efficient.
A 3 phase profile will be used, with end conditions $v_f=0, a_f=0$ and initial conditions set to the current state of the navigation filter.

Now appropriate values of $a_m^-$ and $j_m^-$ must be chosen to completely parameterize the trajectory.
For calculating $\Delta s_{RSTOP}$, the same set of values from normal planning is used.
Note that a static buffer distance, $\Delta s_{buf}$ is added to ensure safety and comfort.
RSTOP is triggered when $\Delta s_{RSTOP} + \Delta s_{buf} >= s_{ped} - s_{veh}$ and the actual available stopping distance $\Delta s_{avail} = s_{ped} - s_{veh}$ is computed.
The trajectory is then recomputed with increasingly higher-magnitude values of $a_m^-$ and $j_m^-$ until $\Delta s_{RSTOP} <= \Delta s_{avail}$.
Should one of the values $a_m^-$ or $j_m^-$ required to fulfill this condition exceed the limits $a_m^{-,max}$ or $j_m^{-,max}$, then limit braking parameters are set such that $a_m^-=a_m^{-,max}$ and $j_m^-=j_m^{-,max}$, and the user is alerted.

@@

>>>>

Next the nominal distance needed to stop $\Delta s_{RSTOP}$ must be computed given the vehicle's current location, speed, and forward acceleration.
The procedure for doing this will be the same as the procedure for planning the RSTOP trajectory later with a few steps omitted, since the planning algorithm is extremely efficient.

Note that a static buffer distance, $\Delta s_{buf}$ is added to ensure safety and comfort.
RSTOP is triggered when $\Delta s_{RSTOP} + \Delta s_{buf} >= s_{ped} - s_{veh}$ and the actual available stopping distance $\Delta s_{avail} = s_{ped} - s_{veh}$ is computed.
Planning and executing the trajectory for coming to a halt is detailed in Sec. \ref{sec:reactivestoptrajectory}.

@@

\subsection{Reactive Stop Trajectories} \label{sec:reactivestoptrajectory}

This is the procedure for determining nominal stopping distance required.
A 3 phase profile will be used, with end conditions $v_f=0, a_f=0$ and initial conditions set to the current state of the navigation filter.

Now appropriate values of $a_m^-$ and $j_m^-$ must be chosen to completely parameterize the trajectory.
For calculating $\Delta s_{RSTOP}$, the same set of values from normal planning is used.

Once the path manager triggers RSTOP, the trajectory is then recomputed with increasingly higher-magnitude values of $a_m^-$ and $j_m^-$ until $\Delta s_{RSTOP} <= \Delta s_{avail}$.
Should one of the values $a_m^-$ or $j_m^-$ required to fulfill this condition exceed the limits $a_m^{-,max}$ or $j_m^{-,max}$, then limit braking parameters are set such that $a_m^-=a_m^{-,max}$ and $j_m^-=j_m^{-,max}$, and the user is alerted.
